Home Nighttime Cough Monitoring

### 2025-07-14 Lilah Melzer/cough_monitor_analysis.qmd
cough monitor updates

    numeric.stats = c("N", "Nmiss", "medianq1q3", "range"),
    cat.stats = c("N", "Nmiss", "countpct"),

@@

```{r results='asis'}
per_person <- agg_counts %>%
  group_by(sid, Diagnosis) %>%
  summarise(
    `Nights` = n(),
    `Nights With Data` = sum(!is.na(Coughs)),
    `Prop. Nights With Data` = sum(!is.na(Coughs)) / n(),
    `Median Coughs per Night` = median(Coughs, na.rm = T),
    `Prop. Nights With Cough` = sum(Coughs > 0, na.rm = T) / n(),
    .groups = "drop"
  )
# Exclude the people with 0 nights of data
per_person <- per_person %>% filter(`Nights With Data` != 0)
t2 <- tableby(
  Diagnosis ~ `Nights` + `Nights With Data` + `Prop. Nights With Data` +
    `Prop. Nights With Cough` + `Median Coughs per Night`,
  data = per_person, control = mycontrols
)
summary(t2, pfootnote = T)
```

>>>>

    numeric.stats = c("N", "medianrange"),
    cat.stats = c("N", "countpct"),

@@

```{r results='asis'}
per_person <- agg_counts %>%
  group_by(sid, Diagnosis) %>%
  summarise(
    `Nights` = n(),
    `Nights With Data` = sum(!is.na(Coughs)),
    `Prop. Nights With Data` = sum(!is.na(Coughs)) / n(),
    `Median Coughs per Night` = median(Coughs, na.rm = T),
    `Prop. Nights With Cough` = sum(Coughs > 0, na.rm = T) / n(),
    `Prop. Nights With 0 Cough` = sum(Coughs == 0, na.rm = T) / n(),
    .groups = "drop"
  )
# Exclude the people with 0 nights of data
per_person <- per_person %>% filter(`Nights With Data` != 0)
t2 <- tableby(
  Diagnosis ~ `Nights` + `Nights With Data` + `Prop. Nights With Data` +
    `Prop. Nights With 0 Cough` + `Prop. Nights With Cough` +
    `Median Coughs per Night`,
  data = per_person, control = mycontrols
)
summary(t2, pfootnote = T)
```
